### 2018-03-06 Maths Notes/Further Pure/FP2/Further Complex Numbers/Further Complex Numbers.tex
FP2 Notes update, loci needs finishing

>>>>

\section{Loci on the complex plane}
\subsection{$\mathbf{|z-z_1|=r}$}
$|z-z_1|=r$ is represented by a circle, centre $(x_1,y_1)$ with a radius r, where $z_1=x_1+iy_1$.\\
This is the same as the Cartesian equation:
$$(x-x_1)^2+(y-y_1)^2=r^2$$
This looks like the graph:\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

\draw (axis cs:1,2) circle [black, radius=3];
    \node[] at (axis cs: 1,2) {$(x_1,y_1)$};
    \node[] at (axis cs: 2,3.3) {$r$};

           \node[anchor=west] (source) at (axis cs:1,2){};
       \node (destination) at (axis cs:3,4.5){};
       \draw[->](source)--(destination);
\end{axis}
\end{tikzpicture}
\subsection{$\mathbf{|z-z_1|=|z-z_2|}$}
$|z-z_1|=|z-z_2|$ is represented by a perpendicular bisector of the line segment joining points $z_1$ and $z_2$\\
\\
To find the Cartesian form, replace z with $x+iy$ and expand, squaring both sides to remove the modulus signs.\\
\\
This looks like the graph:\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-5,ymax=5,xmin=-5,xmax=5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

    \node[] at (axis cs: 1,3) {$z_2$};
    \node[] at (axis cs: 3,1) {$z_1$};
\addplot coordinates { (-4,-4) (4,4) };

\end{axis}
\end{tikzpicture}\\
For cases where there is a constant in front of one of the modulus signs, use the algebraic method to find the Cartesian form, then plot that.
\newpage
\subsection{$\mathbf{\arg(z-z_1)=\theta}$}
$\arg(z-z_1)=\theta$ is represented by the half-line from the fixed point $z_1$, making an angle $\theta$ with a line from the fixed point $z_1$, parallel to the real axis.\\
\\
To find the Cartesian form, replace z with $x+iy$ and separate into the real and imaginary parts. Then use the trigonometric identity $\tan\theta=\dfrac{\textrm{Opposite}}{\textrm{Adjacent}}$ and simplify.\\
\\
When plotting remember that $\theta$ is the angle anticlockwise.\\
\begin{tikzpicture}[scale=0.8]
\begin{axis}[axis lines=middle,ymin=-2.5,ymax=2.5,xmin=-2.5,xmax=2.5,ticks=none]
\pgfplotsset{every tick label/.append style={font=\Large}}

\addplot coordinates { (0,0) (-2,1) };
\draw (axis cs: 0.7,0) arc[radius=80, start angle= 0, end angle= 150];
    \node[] at (axis cs: 0.7,0.7) {\Large $\theta$};
\node[blue] at (axis cs: -2,1.2) {\LARGE $z_1$};

\end{axis}
\end{tikzpicture}
\subsection{$\mathlarger{\mathbf{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}}$}
$\mathlarger{\arg\Big(\frac{z-z_1}{z-z_2}\Big)}$ represents an arc anticlockwise between $z_1$ and $z_2$
